---
title: "Linear Regression Analysis Package"
author: "Kristina Levina and Ingemar Sjostrom"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{linreg-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab5AdvancedR)
```
The package enables to obtain various outputs of the linear regression analysis from the input data. The user is expected to put ´formula´ and ´data´ as parameters to one of the following functions:

1) The function below prints the coefficients of the linear regression analysis of the input data.
```
print1.linreg(formula, data)
```
2) The function below plots the fitted-value-dependence of the residuals and square root of standardised residuals obtained by the linear regression analysis of the input data.
```
plot.linreg(formula, data)
```
3) The function below outputs the coefficients of the linear regression analysis of the input data
```
coef.linreg(formula, data)
```
4) The function below outputs the residuals of the linear regression analysis of the input data
```
resid.linreg(formula, data)
```
5) The function below provides a short summary of the linear regression analysis of the input data
```
summary.linreg(formula, data)
```
6) The function below outputs the predicted values of the linear regression analysis of the input data
```
pred.linreg(formula, data)
```

